Supporting Information

### 2018-04-03 SupportingInformation.Rmd
adding chunk for phylo_data

>>>>

## Phylogenetic data  \label{Phylo_data}
```{r calculation_phylo_data, echo=F, results="hide"}
source("getcopula.R")
phylo_dat<-read.csv("./Data/Anolis/contrasts.csv",header = F)
# Input :
#        data : a dataframe : phylo_dat with dim.=[99 x 14]
#        i, j : column indices of data frame to get bivariate data set, should be (i,j)<=13
#        ploton : logical for option plots of raw data and it's copula representation
# Output : 
#        a cop rank matrix for the raw data
phylo_dat_fn<-function(data,i,j,ploton=T){

  data<-data[,2:dim(phylo_dat)[2]]
  d<-data[,c(i,j)]

  v_phylo<-getcopula(d=d,rankon = T,ploton = F)

  if(ploton==T){
    op<-par(mfrow=c(1,2))
    plot(d[,1],d[,2],col="blue")
    getcopula(d=d,rankon = T,ploton = T)
    par(op)
  }
  return(v_phylo)
}

# This plot I create on temporary basis to see the copula structure between various column of the raw data
# After I know which variables should I look into, I will modify this chunk and add model selection and NPA on that
pdf("./Results/temp_phylo_plot.pdf",width=20, height=20)
op<-par(mfrow=c(13,13))
for(i in c(1:13)){
  for(j in c(1:13)){
    v_phylo<-phylo_dat_fn(data=phylo_dat,i=i,j=j,ploton = F)
    plot(v_phylo[,1],v_phylo[,2],col="red")
    #mtext("(i,j)=(",i,", ",j,")")
    mtext(paste0(" [",i,",",j,"] ", ","," n=",dim(v_phylo)[1]),side = 3,col="blue")
  } 
}
par(op)
dev.off()
```
